---
title: Histogram
author: Ivona Plecevic
date: '2017-10-10'
slug: histogram
categories:
  - Histogram
tags:
  - Histogram
  
---
Here you can see how to make an Histagram!

In this example we want to see the weights of MLB players, through the Master table.

But firstly, we have to install those pakages:

```{r warning=FALSE, message=FALSE}
library(Lahman)
library(sqldf)
library(ggplot2)
```

For this example, we need to use the Master table to gather its data.

```{r}
query<-"SELECT weight 
FROM Master"
result<-sqldf(query)
```

Also, we have to use handy tool ggplot2:
```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="purple",fill="white",bins=50)+
  ggtitle("Body-weight Distribution for Baseball Players")+
  xlab("Weight of player")+
  ylab("Number of players")
```

The histograms can also look a diffrent, because we can change colors and sizes of bins. Here is one example:
```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="purple",fill="white",bins=10)+
  ggtitle("Body-weight Distribution for Baseball Players")+
  xlab("Weight of player")+
  ylab("Number of players")
```

Next example of Histagram help us to see some drastical changes:

```{r}
ggplot()+
  geom_histogram(data=result,aes(x=weight),color="purple",fill="white",bins=100)+
  ggtitle("Distribution of Baseball Player Bodyweight")+
  xlab("Weight of player")+
  ylab("Number of players")
```
